---
title: "Flexdashboard report"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(knitr)

surveys_complete<-read_csv("data/complete_surveys.csv")
```

Column {data-width=650}
--------------------------------------------------------------------

### Small animal survey data

This is a survey of small animals from `r nlevels(as.factor(surveys_complete$plot_id))` plots
from the years `r min(surveys_complete$year)` to `r max(surveys_complete$year)`. Each row is an animal. Each column is an attribute of that animal. The variables recorded are `r names(surveys_complete)`.

### Sex Table
Here is a breakdown of the number of female vs male animals observed in the study
```{r}
kable(surveys_complete%>%
                group_by(sex)%>%
                tally)
```

### Mean weight
The mean weight of all animals surveyed 
is `r mean(surveys_complete$weight, na.rm=TRUE)`.

### Weight vs. Hindfoot length
Species cluster together when plotting weight vs. hindfood length
```{r}
ggplot(data = surveys_complete, 
       aes(x = weight, 
           y = hindfoot_length, 
           color = species_id)) + 
          geom_point(alpha = 0.1,
           aes(color = species_id))
```


