---
title: "Flexdashboard report"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
   
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(knitr)
library(shiny)

surveys_complete<-read_csv("data/complete_surveys.csv")
```

Column {.sidebar}
--------------------------------------------------------------------
```{r inputs, echo=FALSE}
sliderInput("max_weight", label = "Select max weight:",
            min = 0.0, 
            max = max(surveys_complete$weight), 
            value = max(surveys_complete$weight), 
            step = 20)

sliderInput("max_hfl", label = "Select max hindfoot length:",
            min = 0.0, 
            max = max(surveys_complete$hindfoot_length), 
            value = max(surveys_complete$hindfoot_length), 
            step = 20)
```

Column
--------------------------------------------------------------------
### Small animal survey data

This is a survey of small animals from `r nlevels(as.factor(surveys_complete$plot_id))` plots
from the years `r min(surveys_complete$year)` to `r max(surveys_complete$year)`. Each row is an animal. Each column is an attribute of that animal. The variables recorded are `r names(surveys_complete)`.

The mean weight of all animals surveyed 
is `r mean(surveys_complete$weight, na.rm=TRUE)`.

### Sex Table
Here is a breakdown of the number of female vs male animals observed in the study
```{r}
kable(surveys_complete%>%
                group_by(sex)%>%
                tally)
```

Column
--------------------------------------------------------------------

### Weight vs. Hindfoot length
Species cluster together when plotting weight vs. hindfoot length
```{r}
renderPlot(surveys_complete%>%
                filter(weight<=input$max_weight,
                       hindfoot_length<=input$max_hfl)%>%
                ggplot(aes(x = weight,
                           y = hindfoot_length, 
                           color = species_id)) + 
                geom_point(alpha = 0.1,
                           aes(color = species_id)))
```


