---
title: "Markdown Demo"
author: "Tobin Magle"
date: "4/10/2018"
output: html_document
resource_files:
- data/complete_surveys.csv
- data/complete_surveys.csv
- data/complete_surveys.csv
---

```{r setup, include=FALSE}

library(tidyverse)
library(knitr)
library(reticulate)
knitr::knit_engines$set(python = reticulate::eng_python) 

use_condaenv('/home/tmagle/.local/share/r-miniconda/envs/r-reticulate')
surveys_complete<-read_csv("data/complete_surveys.csv")

```

# Small animal survey data

This is a survey of small animals from `r nlevels(as.factor(surveys_complete$plot_id))` plots
from the years `r min(surveys_complete$year)` to `r max(surveys_complete$year)`. Each row is an animal. Each column is an attribute of that animal. The variables recorded are `r names(surveys_complete)`.

# Sex table
Here is a breakdown of the number of female vs male animals observed in the study

```{r, table, echo = FALSE}
kable(surveys_complete%>%
                group_by(sex)%>%
                tally)
```

# Mean weight
The mean weight of all animals surveyed 
is `r mean(surveys_complete$weight, na.rm=TRUE)`.

# Relationship between hindfoot length and weight
We are interested in the relationship between weight and hindfoot length by species. Here is a graph.

```{python graph2, echo=FALSE, warnings = FALSE}


import seaborn as sns
import pandas as pd
import matplotlib.pyplot as plt
import PyQt5
plt.switch_backend('agg') # Very Important in R Markdown with Rocker/VBox

sns.relplot(data=r.surveys_complete,
            x="weight", 
            y="hindfoot_length", 
            alpha = 0.1, 
            hue = "species_id")
plt.show()
```
